Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-01-14 vesicle_code/docs/adhesion/adhesion.tex
some more from yn
added some todos

\todo[inline]{$\sigma$ is overdefined as the Hamacher constant, and the
tension, and possibly the stress}

>>>>

\todo[inline]{$\sigma$ is overdefined as the Hamacher constant, and the
tension, and possibly the stress.  Replace Hamacher constant with $H$.}

\todo[inline]{In the xtensional flow, put a plus sign after the 0.
Indicate the flow with arrows.  Do the same for the shear and Figure 9
(right).}
